---
title: "Assignment 1"
output:
  word_document: default
---
#QA1
#The main purpose of regularization is to simplify models in order to improve their performance. Keeping it as simple as possible decreases the chance of a model being to complex and struggling to generalize. 

#QA2
#A loss function is a function that is trying to minimize an objective in predictive modeling. An example of a loss the function for regression models is root mean square error, RMSE, or the mean absolute error MAE. A example of a common loss function for classification models is log loss, ROC and AUC.

#QA3
#You can’t fully trust this model because of the chance there may be overfitting. A smaller more specific data setDue to a large number of hyperparameters is the perfect candidate for overfitting. The fact that the training error is low also makes me consider the idea of overfitting because typically a lower training model means themodel is probably more complex. There is a greater likelihood that the model could lose its ability to generalize.

#Q4
#The lambda parameter controls the amount of regularization of a model. The lambda parameter balances the minimization and error of a model to find an optimal solution. In a Lasso regression model the lambda parameter minimize the absolute sum values of coefficients while in Ridge Regression models minimizes the sum square of the error terms. 


```{r}
library(ISLR)  
library(dplyr)  
library(glmnet)
library(caret) 

#Problem QB1

Carseats_Filtered <- Carseats %>% select("Sales", "Price","Advertising","Population","Age","Income","Education") 
preProcess(Carseats_Filtered)

y <- Carseats$Sales
x <- as.matrix(Carseats[, c('Price', 'Advertising', 'Population', 'Age', 'Income', 'Education')])
#Fit Models 

fit = glmnet(x,y)
plot(fit)

```

```{r}
print(fit)

```
```{r}
coef(fit, s=1)
```
```{r}
#Predictions
nx = matrix(rnorm(12*6),12,6)
predict(fit,newx=nx,s=c(.1,.05))
```

```{r}
#Cross Validation
cvfit = cv.glmnet(x,y)
plot(cvfit)
```
```{r}
cvfit$lambda.min
```
```{r}
cvfit$lambda.1se
```
```{r}
coef(cvfit, s = "lambda.min")
```
```{r}
predict(cvfit, newx = x[1:6,], s = "lambda.min")
```

```{r}
cvfit = cv.glmnet(x, y, type.measure = "mae", nfolds = 5)
coef(cvfit, s = "lambda.min")
```
```{r}
#Build Lasso 
fit.lasso <- glmnet(x, y, alpha = 1)
plot(fit.lasso, xvar = "lambda")
```
```{r}
plot(cv.glmnet(x, y, alpha=1))
```
```{r}
#Question 2
 
coef(cvfit, s = "lambda.min")
```
```{r}
predict(cvfit, newx = x[1:6,], s ="lambda.min")
# The coefficient for the price in the best model is 8.2777. 
```
```{r}
#Question 3
coef(fit, s=1)
```
```{r}

coef(fit,s=0.01)
```
```{r}
coef(fit, s=0.1)
```
#All 6 attributes stay in the model if the lambda is set to 0.01. Where as only 5 stayin the model if the lambda is set to 0.10. I would expect less variables to stay in the model as you increase the lambda. 

```{r}
#Question 4
fit.elnet <- glmnet(x,y, alpha = 0.6)
plot(fit.elnet, xvar = "lambda")
```
```{r}
plot(cv.glmnet(x,y,alpha=.06))
```
```{r}
print(fit.elnet)
```
# The Optimal lambbda is 0.00654 in this model. 

```{r}
for (a in seq(0,1, by=0.1)) {
  cvfit=cv.glmnet(x, y, alpha=a)
  print(paste0("alpha is ", a, " and best MSE is " ,min(cvfit$cvm)))
} 
```

